### 2017-10-23 paper/sections/3_posix_overheads.tex
paper: carlos feedback
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: fill in all CITEMEs, hammer on main points
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% CITEME PDSW paper
In our examination of the overheads of POSIX IO we benchmark and analyze CephFS,
the file system that uses Ceph's object store ({\it i.e.} RADOS) to store its
data and metadata. To show how the file system behaves under high metadata load
we use a create-heavy workload. Create-heavy workloads are studied the most in
HPC research because of the checkpoint/restart use case but they also happen to
stress the underlying storage system the most.  During this process we
discovered, based on the analysis and breakdown of costs, that durability and
consistency have high overhead but we urge the read to keep in mind that this
file system is an implementation of one set of design decisions and our goal
here is to highlight the effect that those decisions have on performance.

% CITE ME Lustre paralle
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage (combined CPU, network, and disk)
because of the number of RPCs needed for consistency and durability. The RPCs
are also serialized because the metadata server is single threaded; although
naive, this design is common because of the complexity of multi-threaded
metadata servers.  Traditional file system techniques for improving
performance, such as caching inodes, do not help for create-heavy workloads.
In this section, we quantify the costs of consistency and durability in CephFS.
At the end of each subsection we compare the approach to ``decoupled
namespaces", the technique in related work that detaches subtrees from the
global namespace to relax consistency/durability guarantees.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{Runtime normalized to no journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.2\linewidth]{graphs/behavior-interfere.png}
      \caption{Interference forces \texttt{lookup()}s}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{Interference hurts variability}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{The overhead of global durability and strong consistency in CephFS.
  (a) shows the effect of different journal segment sizes, which are streamed
  into the object store for fault tolerance. (b) and (c) show that when a second
  client ``interferes", capabilities are revoked and metadata servers do more
  work.  \label{fig:overhead}}
\end{figure*}

@@

% CITEME: SSTables
\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
to the best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then, on restart,
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later flushed to the underlying
distributed file system.

>>>>

In our examination of the overheads of POSIX IO we benchmark and analyze
CephFS, the file system that uses Ceph's object store ({\it i.e.} RADOS) to
store its data and metadata. To show how the file system behaves under high
metadata load we use a create-heavy workload.  During this process we
discovered, based on the analysis and breakdown of costs, that durability and
consistency have high overhead but we urge the reader to keep in mind that this
file system is an implementation of one set of design decisions and our goal
here is to highlight the effect that those decisions have on performance.

Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage (combined CPU, network, and disk)
because of the number of RPCs needed for consistency and durability. The RPCs
are also serialized because the metadata server is single threaded; although
na\"{\i}ve, this design is common because of the complexity of multi-threaded
metadata servers~\cite{konstantinos:pdsw2014-lustre-metadata}.  Traditional
file system techniques for improving performance, such as caching inodes, do
not help for create-heavy workloads.  In this section, we quantify the costs of
consistency and durability in CephFS.  At the end of each subsection we compare
the approach to ``decoupled namespaces", the technique in related work that
detaches subtrees from the global namespace to relax consistency/durability
guarantees.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{Runtime normalized to no journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.2\linewidth]{graphs/behavior-interfere.png}
      \caption{Interference forces \texttt{lookup()}s}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{Interference hurts variability}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{The overhead of durability and strong consistency in CephFS.
  (a) shows the effect of different journal segment sizes, which are streamed
  into the object store for fault tolerance. (b) and (c) show that when a second
  client ``interferes", capabilities are revoked and metadata servers do more
  work.  \label{fig:overhead}}
\end{figure*}

@@

\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS, to the
best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an
SSTable~\cite{ren:atc2013-tablefs}) then those batched metadata operations are
lost. For DeltaFS, if the client fails then, on restart, the computation does
the work again -- since the snapshots of the namespace are never globally
consistent and there is no ground truth.  On the server side, BatchFS and
DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which initially
reside in memory but are later flushed to the underlying distributed file
system.

### 2017-10-23 paper/sections/6_results.tex
paper: jeff comments/citations and fix figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: fill in all CITEMEs, hammer on main points
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% CITEME xiao:socc2015-shardfs CITEME HADOOP
First we show how we can build application-specific subtrees by composing
mechanisms and that this approach results in more a scalable global
namespace. We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
But the workload also appears in cloud workloads, where systems like Hadoop use
the file abstraction to exchange work units to workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  We use this as a microbenchmark because it
allows us to control the size of the log, since each create creates a single
journal event. The workload is clients creating 100K files in private
directories in the same global namespace.

@@

\textbf{Takeaway}: the ability to couple well-established techniques to
specific applications allows the global namespace to scale further and perform
better.

@@

% CITEME
The final use case shows how the API gives users fine-grained control of the
consistency semantics for niche or {\it ad-hoc} workflows.  Scientists use the
file system to check the progress of jobs using \texttt{ls}~\cite{CITEME}. The
number of files or size of the files is indicative of the progress. This
practice is not too different from systems that use the file system to manage
the progress of jobs; Hadoop writes to temporary files, renames them when
complete, and creates a ``DONE" file to indicate to the runtime that the task
did not fail and should not be re-scheduled on another node. In this scenario,
Cudele users will not see the progress of decoupled namespaces since their
updates are not globally visible.  To help scientists judge the progress of
their jobs, Cudele clients have a ``namespace sync" that sends batches of
updates back to the global namespace at regular intervals.

>>>>

First we show how we can build application-specific subtrees by composing
mechanisms and that this approach results in more a scalable global namespace.
We start with clients creating files in private directories because this
workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
But the workload also appears in cloud workloads~\cite{xiao:socc15-shardfs},
where systems like Hadoop use the file abstraction to exchange work units to
workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  We use this as a microbenchmark because it
allows us to control the size of the log, since each create creates a single
journal event. The workload is clients creating 100K files in private
directories in the same global namespace.

@@

\textbf{Takeaway}: the ability to couple well-established techniques to
specific applications allows the global namespace to scale further and perform
better. In our case, RPCs overwhelm the system but decoupling/shipping a
journal of updates improves scalability by 2\(\times\).

@@

The final use case shows how the API gives users fine-grained control of the
consistency semantics for niche or {\it ad-hoc} workflows.  Scientists use the
file system to check the progress of jobs using \texttt{ls} even though this
operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache} . The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Hadoop writes to temporary files,
renames them when complete, and creates a ``DONE" file to indicate to the
runtime that the task did not fail and should not be re-scheduled on another
node. In this scenario, Cudele users will not see the progress of decoupled
namespaces since their updates are not globally visible.  To help scientists
judge the progress of their jobs, Cudele clients have a ``namespace sync" that
sends batches of updates back to the global namespace at regular intervals.
